### 2023-01-29 paper-reviews/papers-2023.tex
Add optical AI paper

    \item As practice shows creating a concise reproducer for a bug is sometimes as complex as fixing a bug. Compiler bugs can be especially hard to report as they are usually observed on real and rather big projects. Even relatively small \href{https://yulyugin.github.io/blog/2022/icc-bug}{compiler bug} reproducers could be hard to analyze and report. Authors of the paper tried to address this important issue by implementing an automatic test case reducers for C:

@@

>>>>

    \item As practice shows creating a concise reproducer for a bug is sometimes as complex as fixing the bug. Compiler bugs can be especially hard to report as they are usually observed on real and rather big projects. Even relatively small \href{https://yulyugin.github.io/blog/2022/icc-bug}{compiler bug} reproducers could be hard to analyze and report. Authors of the paper tried to address this important issue by implementing an automatic test case reducers for C:

@@

\section*{Machine Learning}
\begin{itemize}
    \item Optical computing for AI moves closer to commercialization. Startups originating from MIT and Princeton demonstrate interesting optical computing for AI solutions. The systems are targeting convolutional neural networks. 2D filtering is equal to 2D convolution. The approach is aimed to reduce heat and power consumption and of course improve performance simultaneously. One of the main problems so far is optical to electrical and electrical to optical signal conversion. Solutions for the problem seems to be a key for high performance at the moment. The article also contains a link to a scientific paper with more details.

    \cite{Wheeler:Optical-AI:2019}.
\end{itemize}
